Long term cloud enhancement events of global solar irradiance over Thessaloniki

### 2024-05-26 article/article.tex
Commit 2024-05-26 22:14

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Downward shortwave solar irradiance enhancement by clouds.},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

@@

  \title{Downward shortwave solar irradiance enhancement by clouds.}
    \author[LAP]{Athanasios N. Natsis%
  \corref{cor1}%
  \fnref{1}}
   \ead{natsisphysicist@gmail.com} 
    \author[LAP]{Alkiviadis Bais%
  %
  }
   \ead{abais@auth.gr} 
    \author[LAP]{Charikleia Meleti%
  %
  \fnref{2}}
   \ead{meleti@auth.gr} 
      \affiliation[LAP]{
    organization={Laboratory of Atmospheric Physics, Physics Department,
Aristotle University of
Thessaloniki},city={Thessaloniki},postcode={54124},country={Greece},}
    \affiliation[Another University]{
    organization={Department},addressline={A street
29},city={Manchester,},postcode={2054 NX},state={State},country={The
Netherlands},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{This is the first author footnote.}
    \fntext[2]{Another author footnote.}

@@

\begin{itemize}
\tightlist
\item
  Phenomenon
\item
  Effects
\item
  bibliography
\item
  our approach
\item
  our results
\end{itemize}

CE: cloud enhancement cases one minute

@@

\(\text{GHI}_\text{CSm}\): modeled clear sky one minute global
horizontal irradiance

@@

The shortwave solar irradiance, reaching Earth's surface, is the main
energy source of the atmosphere and biosphere and drives and governs the
climate \citep{Gray2010}. It has direct practical application, in
different industries, like energy production and agriculture method. The
variability of its intensity, can cause difficulties in predicting the
yield, and designing the specifications of the appropriate equipment. A
lot of research has been focused on predicting the renewable energy
production in a fine timescale and in near real-time (for a review see
\citet{Inman2013}; \citet{Graabak2016}).

A big aspect of this variability is the interaction with the clouds. In
general, clouds absorb part of the solar irradiance, but under certain
conditions, can enhance the total shortwave irradiance reaching the
ground. This effect, can locally increase the observed total shortwave
irradiance higher than the expected clear sky irradiance {[}see
references therein{]}.

>>>>

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Long term cloud enhancement events of global solar irradiance over Thessaloniki},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

@@

  \title{Long term cloud enhancement events of global solar irradiance
over Thessaloniki}
    \author[LAP]{Athanasios N. Natsis%
  \corref{cor1}%
  \fnref{1}}
   \ead{natsisphysicist@gmail.com} 
    \author[LAP]{Alkiviadis Bais%
  %
  }
   \ead{abais@auth.gr} 
    \author[LAP]{Charikleia Meleti%
  %
  \fnref{2}}
   \ead{meleti@auth.gr} 
      \affiliation[LAP]{
    organization={Laboratory of Atmospheric Physics, Physics Department,
Aristotle University of
Thessaloniki},city={Thessaloniki},postcode={54124},country={Greece},}
    \affiliation[Another University]{
    organization={Department},addressline={A street
29},city={Manchester,},postcode={2054 NX},state={State},country={The
Netherlands},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{This is the first author footnote.}
    \fntext[2]{Another author footnote.}

@@

We studied the enhancement of the global horizontal irradiance (GHI),
over Thessaloniki, for the period 1993 -- 2023, on one minute average
records. We identify the cloud enhancement events (CE), by creating an
appropriate clear sky irradiance reference with the use of a radiation
transfer model, and aerosol optical depth (AOD) data, from the AERONET,
and a collocated Brewer photospectrometer. We found that there is a
trend of CE cases of \(45.6\pm 21.9\,\text{cases}/\text{year}\), and a
mean total energy change, of the CE events by
\(116.9\pm 67.8\,\text{kj}/\text{year}\) with the peak of the CE events
are observed during May and June. An analysis of the total duration of
CE events, showed that durations longer than 5 minutes are very rare,
with exceptions lasting over an hour. We have detected enhancements over
the total solar irradiance, without exceeding the maximum values
reported for other sites, with more favorable CE conditions.

~ ~ CE: cloud enhancement cases one minute

@@

\(\text{GHI}_\text{CSm}\): modelled clear sky one minute global
horizontal irradiance

@@

The shortwave solar irradiance, reaching Earth's surface, is the main
energy source of the atmosphere and the biosphere, and drives and
governs the climate \citep{Gray2010}. It has direct practical
application, in industries like energy and agricultural production. The
variability of its intensity, can cause difficulties in predicting the
yield, and designing the specifications of the appropriate equipment.
Significant portion of research has been focused on predicting the
renewable energy production in a fine timescale and in near real-time
(for a review see \citet{Inman2013}; \citet{Graabak2016}).

A big aspect of this variability is the interaction of GHI with the
clouds. In general, clouds absorb part of the solar irradiance, but
under certain conditions, can enhance the total shortwave irradiance
reaching the ground. This effect, can locally increase the observed GHI,
even higher than the expected clear sky irradiance {[}see references
therein{]}.
